A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
update on model coefficient
modified predictor variables

To ensure high data quality, we filtered the dataset to include polls with a numeric grade of 2.7 or above and focused only on polls conducted after July 21, 2024, the date of Harris' declaration of candidacy. The filter helped limit bias from older polls from when Joe Biden was the Democratic nominee, which may not reflect the current voter sentiment.

@@

The main variable we aim to forecast is the pct variable, which represents the proportion of the vote a candidate received in a poll.@tbl-pct-cleaned and @fig-pct-cleaned shows the summary statistics and distribution of pct variable in a filtered dataset that only comprises of votes from relatively high-quality polling organizations. We also get the popular vote predictions for each candidate using the predict() function and add this to the dataset as the predicted_pct variable. We have showed the summary statistics and distribution for predicted_pct in @tbl-pct-predicted and @fig-pct-predicted, respectively.

@@

### Type of Pollster {sec-data-pollster}

The pollster variable was selected to consider the effect of changes in pollster on the observed variable. The pollster variable represents the polling organization that conducted the poll. The distribution of polling counts for different pollsters in @fig-pollster suggests that the data is dominated by three pollsters: Ipsos, YouGov and Siena/NYT. Further analysis is needed in their polling methodology to determine potential biases.

```{r}
#| label: tbl-pollster
#| fig-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pollster' variable
summary_stats <- prediction %>%
  summarize(
    count(pollster, name = "Count")
  )

@@

# Plot distribution using histogram
ggplot(prediction, aes(x = pollster)) +
  geom_bar(fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Pollster",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Population Type {sec-data-populationtype}

@@

```{r}
#| label: tbl-populationtype
#| fig-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

@@

### Poll Recency {sec-data-pollrecency}

Poll Recency, shown through the variable `recent_poll`, labels any polls that have been conducted in the last 30 days as Recent and any polls collected before that are labeled Older. Based on our results shown in @tbl-recency, there are 32 less polls collected in the last 30 days than before. This introduces biases in responses as older responses are more represented in our model. In rapidly changing political environments, public opinion can shift dramatically due to major events, debates or crises, making recent data crucial for accurate modeling.The distribution of this variable can also be found in @fig-recency.

```{r}
#| label: tbl-recency
#| fig-cap: Number of polls that were collected within 30 days and after
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

@@

The first step in our process involved selecting a reliable dataset for model development. Here, we utilized high-quality national polling data gathered after Harris’s campaign announcement. We filtered the dataset to include polls with a numeric grade of 2.7 or above, ensuring data quality, and focused only on polls conducted after July 21, 2024, the date of Harris’s declaration of candidacy. This filter helps limit bias from older polls that may not reflect the current voter sentiment.

@@

@fig-coefficient-estimates represents the model coefficients, with error bars indicating the confidence interval for each estimate. Positive coefficients suggest that specific pollsters or demographic characteristics increase Harris’s predicted vote share. For example, the 'CES / YouGov' pollster shows a positive impact, while 'Siena/NYT' has a slight negative effect. These error bars help contextualize the reliability of each predictor.

>>>>

To ensure high data quality, we filtered the dataset to include polls with a numeric grade of 3.0 and focused only on polls conducted after July 21, 2024, the date of Harris' declaration of candidacy. The filter helped limit bias from older polls from when Joe Biden was the Democratic nominee, which may not reflect the current voter sentiment.

@@

The main variable we aim to forecast is the pct variable, which represents the proportion of the vote a candidate received in a poll. @tbl-pct-cleaned and @fig-pct-cleaned shows the summary statistics and distribution of pct variable in a filtered dataset that only comprises of votes from relatively high-quality polling organizations. We also get the popular vote predictions for each candidate using the predict() function and add this to the dataset as the predicted_pct variable. We have showed the summary statistics and distribution for predicted_pct in @tbl-pct-predicted and @fig-pct-predicted, respectively.

@@

### Type of Pollster {#sec-data-pollster}

The pollster variable was selected to consider the effect of changes in pollster on the observed variable. The pollster variable represents the polling organization that conducted the poll. The distribution of polling counts for different pollsters in @fig-pollster suggests that the data is dominated by two pollsters: YouGov and Siena/NYT. Further analysis is needed in their polling methodology to determine potential biases.

```{r}
#| label: tbl-pollster
#| tbl-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pollster' variable
summary_stats <- prediction %>%
  count(pollster, name = "Count")

@@

# Plot distribution using histogram
ggplot(prediction, aes(x = pollster)) +
  geom_bar(fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Pollster",
       y = "Count") +
  coord_flip() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Population Type {#sec-data-populationtype}

@@

```{r}
#| label: tbl-populationtype
#| tbl-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

@@

### Poll Recency {#sec-data-pollrecency}

Poll Recency, shown through the variable `recent_poll`, labels any polls conducted in the last 30 days as Recent and any polls collected before that are labeled Older. Based on our results shown in @tbl-recency, 19 more polls have been collected in the last 30 days than before. This introduces biases in responses as recent responses are more represented in our model. In rapidly changing political environments, public opinion can shift dramatically due to major events, debates, or crises, making recent data crucial for accurate modeling. The distribution of this variable can also be found in @fig-recency.

```{r}
#| label: tbl-recency
#| tbl-cap: Number of polls that were collected within 30 days and after
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

@@

The first step in our process involved selecting a reliable dataset for model development. Here, we utilized high-quality national polling data gathered after Harris’s campaign announcement. We filtered the dataset to include polls with a numeric grade of 3.0, ensuring data quality, and focused only on polls conducted after July 21, 2024, the date of Harris’s declaration of candidacy. This filter helps limit bias from older polls that may not reflect the current voter sentiment.

@@

@fig-coefficient-estimates represents the model coefficients, with error bars indicating the confidence interval for each estimate. Positive coefficients suggest that specific pollsters or demographic characteristics increase Harris’s predicted vote share. For example, the 'populationVoters' shows a positive impact, while most of the pollsters has a slight negative effect. These error bars help contextualize the reliability of each predictor.
